H0LiCOW: correlation between black hole mass and host galaxy luminosity

### 2020-02-20 manuscript/manuscript.tex
Upload manuscript

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% my commands
\newcommand{\lcdm}{$\Lambda$CDM}
\newcommand{\hst}{{\it HST}}
\newcommand{\efr}{$R_{\mathrm{eff}}$}
\newcommand{\galfit}{{\sc Galfit}}
\newcommand{\mbh}{$\mathcal M_{\rm BH}$}
\newcommand{\lhost}{$L_{\rm host}$}
\newcommand{\mr}{$Mag_{\rm ~R}$}
\newcommand{\halpha}{${\it H}\alpha$}
\newcommand{\hbeta}{${\it H}\beta$}
\newcommand{\sersic}{S\'ersic}
\newcommand{\lenstronomy}{{\sc Lenstronomy}}
\newcommand{\reff}{{$R_{\mathrm{eff}}$}}
\newcommand{\kmsMpc}{km~s$^{\rm -1}$~Mpc$^{\rm -1}$}
\newcommand{\kms}{\ifmmode{\,\rm{km}\, \rm{s}^{-1}}\else{$\,$km$\,$s$^{-1}$}\fi}
\newcommand{\sigstar}{{$\sigma_*$}}
\newcommand{\mstar}{{$M_*$}}
\newcommand{\Mgii}{Mg$_{\rm II}$}
\newcommand{\Civ}{C$_{\rm IV}$}
%\newcommand{\farcs}{\mbox{\ensuremath{.\!\!^{\prime\prime}}}}% fractional arcsecond symbol: 0.''0
\newcommand{\sam}{\texttt{SAM}}
\newcommand{\mbii}{\texttt{MBII}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\ding}[1]{\textcolor{red}{[{\bf Xuheng}: #1]}}
\newcommand{\todo}[1]{\textcolor{red}{[{\bf Todo}: #1]}}  
\newcommand{\aklant}[1]{\textcolor{blue}{[{\bf AKB}: #1]}} 
\newcommand{\red}[1]{{ \textcolor{red}{#1}}}
\newcommand{\blue}[1]{{ \textcolor{blue}{#1}}}
\newcommand{\pink}[1]{{ \textcolor{magenta}{#1}}}

@@

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[lens source reconstruction]{H0LiCOW xxx: correlation between black hole mass and host galaxy luminosity}

@@

\section{Sample Selection}
The eight lens systems are selected from our H0LiCOW collaboration including HE~0435$-$1223, RXJ~1131$-$1231, WFI~2033$-$4723, HE~1104$-$1805, SDSS~1206$+$4332, SDSS~0246$-$0825, HE~0047$-$1756 and HS~2209$+$1914. For conciseness, we abbreviate each lens name to four digits (e.g., RXJ~1131$-$1231 to RXJ~1131). In \citet{Ding2017a}, the simulation exercise has been performed to understand the fidelity of the source reconstruction based on these eight systems and verified that the host inference is trustworthy when its magnitude are brighter than 20 magnitude, 2$-$4 magnitudes dimmer than the AGN. The detailed information of the observations for these eight systems are given in Table~1 therein.

Rather than infer the host properties from the side produces. 
We focus on source reconstruction in this paper, 
%[]The comparison sample (32 QSO paper)
To expend the sample size, we select the recent efforts by Ding2019, including 32 QSO at redshift  range 1.2<z<1.9, with the local sample.

\section{Surface photometry}
We describe the measurement of the host galaxy in this section. We use adopt the lensing techniques to reconstruct the host galaxy and recover the host magnitude in the source plane. We then obtain the color of the host to derive the rest-frame R band magnitude and estimate the stellar mass.

\subsection{Lensing host reconstruction}
Lensing modeling technique.

[] We define the light profile of the source and lensing galaxy can be described by Sersic profile. The deflector mass are described by the power law.

[] We adopt the \lenstronomy~to perform the modeling task. The detail of the fitting settings: gamma as 1.9, 2.0, 2.1. The mask. Two approaches including QSO mask and PSF reconstruction. Subgrid with 2 and 3 are selected to describe the Sersic profile.

[] Top rank result combined to get the inference of the host galaxies and the way of weighting flux to get magnitude.

@@

\subsubsection{HE0435}
The results of HE0435. A table to summarize the fitting results. The inference of the observed magnitude, Reff and sersic.

@@

@@

We summarized the inference for the eight systems in the table.
name--Setts--BestFitChisq--Totalflux--Reff--Sersicn--magnitude

\subsection{k-correction and stellar mass estimates}
For those ones have multibands. For those only have one bands.

@@

\section{Black Hole mass estimates}
We use viral method to estimate the mass of the black hole. The board-line adopted. We aim to adopt the self-consistent to recalibrate the \mbh~of our sample. [] The recipes. [] The board lines and the resulting BH mass and listed in the table.

@@

Selection effect? We only select 8 sample?

The last numbered section should briefly summarize what has been done, and describe
the final conclusions which the authors draw from their work.

\section{Discussion and Conclusion}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% my commands
\newcommand{\lcdm}{$\Lambda$CDM}
\newcommand{\hst}{{\it HST}}
\newcommand{\efr}{$R_{\mathrm{eff}}$}
\newcommand{\galfit}{{\sc Galfit}}
\newcommand{\mbh}{$\mathcal M_{\rm BH}$}
\newcommand{\lhost}{$L_{\rm host}$}
\newcommand{\mr}{$Mag_{\rm ~R}$}
\newcommand{\halpha}{${\it H}\alpha$}
\newcommand{\hbeta}{${\it H}\beta$}
\newcommand{\sersic}{S\'ersic}
\newcommand{\lenstronomy}{{\sc Lenstronomy}}
\newcommand{\reff}{{$R_{\mathrm{eff}}$}}
\newcommand{\kmsMpc}{km~s$^{\rm -1}$~Mpc$^{\rm -1}$}
\newcommand{\kms}{\ifmmode{\,\rm{km}\, \rm{s}^{-1}}\else{$\,$km$\,$s$^{-1}$}\fi}
\newcommand{\sigstar}{{$\sigma_*$}}
\newcommand{\mstar}{{$M_*$}}
\newcommand{\Mgii}{Mg$_{\rm II}$}
\newcommand{\Civ}{C$_{\rm IV}$}
%\newcommand{\farcs}{\mbox{\ensuremath{.\!\!^{\prime\prime}}}}% fractional arcsecond symbol: 0.''0
\newcommand{\sam}{\texttt{SAM}}
\newcommand{\mbii}{\texttt{MBII}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\ding}[1]{\textcolor{red}{[{\bf Xuheng}: #1]}}
\newcommand{\todo}[1]{\textcolor{red}{[{\bf Todo}: #1]}}  
\newcommand{\red}[1]{{ \textcolor{red}{#1}}}
\newcommand{\blue}[1]{{ \textcolor{blue}{#1}}}
\newcommand{\pink}[1]{{ \textcolor{magenta}{#1}}}

@@

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[lens source reconstruction]{H0LiCOW: correlation between black hole mass and host galaxy luminosity}

@@

\section{Sample Selection}
We adopt the eight lens systems from our H0LiCOW collaboration including HE~0435$-$1223, RXJ~1131$-$1231, WFI~2033$-$4723, HE~1104$-$1805, SDSS~1206$+$4332, SDSS~0246$-$0825, HE~0047$-$1756 and HS~2209$+$1914. For conciseness, we abbreviate each lens name to four digits (e.g., RXJ~1131$-$1231 to RXJ1131). In \citet{Ding2017a}, the simulation exercise has been performed to understand the fidelity of the source reconstruction based on these eight systems and verified that the host inference is trustworthy when its magnitude are brighter than 20 magnitude, 2$-$4 magnitudes dimmer than the AGN. The detailed information of the observations for these eight systems are given in Table~1 therein~\ding{Maybe we can re-summarized it again here}. We analyzed the HST imaging data of the sample and the observation has been introduced by~\citet{Ding2017a}. Moreover, three quadruply-imaged AGNs (HE0435, RXJ1131 and WFI2033) have HST imaging data at multi-bands from which we could infer the color of the host galaxy and obtain more accurate stellar template.

%[]The comparison sample (32 QSO paper)
To exam the evolution of the lensed system, we aim to compare.... expend the sample size and the data resolution, we adopt the recent efforts by~\citet{Ding2020}, including 32 QSO at redshift range $1.2<z<1.9$, with the local sample.

\section{Surface photometry}
We describe the reconstruction of the lensed host galaxy in this section. For part of the lensed systems, the lens models have been derived with host galaxies reconstructed ref[]. Aiming at the time-delay cosmography, these works focused on deriving the precise and accurate lens models, while the reconstructed the host galaxy is only a by-product. Thus, in this work, we apply our own approach to infer the photometry of the host galaxy in the source plane. As will show, we compare our inference to the previous ones for cross check purpose.

%We then obtain the color of the host to derive the rest-frame R band magnitude and estimate the stellar mass.

\subsection{Lens model inference and host reconstruction}
We simultaneously carry out the fitting process to derive the lens model, subtract the central AGN light and reconstruct the host galaxy in the source plan. We follow the common practice and assume the photometry of the galaxies (including the lensing galaxy and source galaxy) follows the 2-D elliptical \sersic\ profile, which defines the host flux as consistent to the comparison sample. The bright AGNs are unsolved and described by a scaled PSF. We adopt the elliptical power-law models to describe the surface mass density of the deflector.

%The one of the fitting setting 
[] We adopt the \lenstronomy~ref[] to perform the modeling task. We draw the mask to define the fitting region. The nearby object are considered as extended source and fitted as \sersic.

%Different settings to do the rank.
[] We cut out the available PSFs in the files. Two approaches including QSO mask and PSF reconstruction. Subgrid with 2 and 3 are selected to describe the Sersic profile.  The detail of the fitting settings: gamma as 1.9, 2.0, 2.1.

%How to do the rank.
[] Top rank result combined to get the inference of the host galaxies and the way of weighting flux to get magnitude.

@@

\subsubsection{HE0435}
The results of HE0435. A table to summarize the fitting results. The inference of the observed magnitude, Reff and sersic. 
Comparison to the previous inference.

The other two band.

@@

\subsubsection{SDSS1206}

\subsubsection{HE1104}

\subsubsection{SDSS0246}

\subsubsection{HE0047}

\subsubsection{HS2209}

@@

We summarized the inference for the eight systems in the table.
name--Setts--BestFitChisq--Totalflux-- Host ratio --Reff--Sersicn--magnitude - Stellar mass

\subsection{Stellar mass estimates}
For those ones have multi-bands, we attempt to infer the color of the host in the image plane.

@@

\section{Black Hole mass estimates}
We use viral method to estimate the mass of the black hole. The board-line adopted. We aim to adopt the self-consistent to recalibrate the \mbh~of our sample. 
[] The recipes. [] The board lines and the resulting BH mass and listed in the table. []The summarizing table.

@@

\ding{Do we consider the Selection effect? We only select 8 sample? Maybe we only over plot them together and see if the results are self-consistent?}

\section{Discussion and Conclusion}
[] This work confirm the bright future of lensing.
